Data cleaning and processing script

### 2023-03-17 code/processing_code/processing.qmd
model building

```{r}
wbe_samp <- wbe_br %>%
  group_by(date, facility) %>% 
  dplyr::summarise(
    n.pos = sum(!is.na(bio.ct.mean)),
    n.miss = sum(is.na(bio.ct.mean)),
    pos_rate_tr = mean(pos_rate_tr)) %>%
  mutate_all(function(x){ifelse(is.nan(x), NA, x)}) %>% 
  ungroup() %>% 
  mutate(prop.pos = n.pos/(n.pos+n.miss)*100)
wbe_samp
saveRDS(wbe_samp, here("data/processed_data/prop_pos_sample.rds"))
```

>>>>

```{r}
wbe_samp <- wbe_br %>%
  group_by(date, facility) %>% 
  dplyr::summarise(
    n.pos = sum(!is.na(bio.ct.mean)),
    n.miss = sum(is.na(bio.ct.mean)),
    pos_rate_tr = mean(pos_rate_tr)) %>%
   mutate(prop.pos = n.pos/(n.pos+n.miss)*100) %>% 
  #mutate_all(function(x){ifelse(is.nan(x), NA, x)}) %>% 
  ungroup()

wbe_samp
saveRDS(wbe_samp, here("data/processed_data/prop_pos_sample.rds"))
```

### Combine all data: wastewater, clinical cases, percent positive

```{r}
final_data <- full_join(all_data, wbe_samp, by = c("date", "facility"))
saveRDS(final_data, here("data/processed_data/final_combined_data.RDS"))
```
